---
title: "p8105_hw6_nt2607"
output: github_document
date: "2022-12-01"
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse)
library(p8105.datasets)
library(readr)
library(purrr)
library(modelr)
library(mgcv)
library(corrplot)
library(polycor)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)

```

### Problem 1

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.

```{r Loading the data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

Step 1. Fit the regression model 
Step 2. Check r-squared for the model
Step 3. Compute the log(β̂ 0∗β̂ 1)

```{r single}
#Fit regression
bootstrap_reg = lm(tmax ~ tmin, data = weather_df)
#Check r-squared for the model
bootstrap_reg %>% 
  broom::glance() %>% 
  select(r.squared) %>% 
  knitr::kable()

#Compute the log(β̂ 0∗β̂ 1̂) 
bootstrap_reg %>% 
  broom::tidy() %>% 
  select(term, estimate) %>%
  mutate(
    term = case_when(
      term == "(Intercept)" ~ "intercept",
      term == "tmin" ~ "tmin")) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
    ) %>% 
  mutate( alpha_beta = log(intercept*tmin))
```

Now build a bootstrap model for 5000 samples doing everything above.

```{r bootstrap}
bootstrap_weather_df =
weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
         square = map(models, broom::glance),
         results = map(models, broom::tidy)
         ) %>% 
  select(-strap, -models)
```

For each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

For r-squared 
```{r plot and df 1}
dist_plot_1_df =
bootstrap_weather_df %>% 
  unnest(square) %>% 
  janitor::clean_names() %>% 
  select(r_squared)  # Step 5. produce estimates of these r-squared quantities.
  
dist_plot_1 =   
  dist_plot_1_df %>% 
  ggplot(aes(x = r_squared)) +
  geom_density()
dist_plot_1
```

Description - From the plot we can see that the r-squared values are almost normally distributed.

For  log(β̂ 0∗β̂ 1)
```{r df 2}
dist_plot_2_df =
bootstrap_weather_df %>% 
  unnest(results) %>% 
  janitor::clean_names() %>%
  select(id, term, estimate) %>% 
mutate(
    term = case_when(
      term == "(Intercept)" ~ "intercept",
      term == "tmin" ~ "tmin")) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate",
    id_cols = id
    ) %>% 
  mutate( alpha_beta = log(intercept*tmin)) %>% 
  select(alpha_beta) #produced estimates of log(β̂ 0∗β̂ 1)quantities
```

Plot the distribution of the log (β̂ 0∗β̂1) quantities

```{r plot 2}
dist_plot_2 = 
  dist_plot_2_df %>% 
  ggplot(aes(x = alpha_beta)) +
  geom_density() 
dist_plot_2
```

Description - From the plot we can see that the log of alpha*beta values are almost normally distributed. 

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1).

Confidence Intervals for r-squared value and  log(β̂ 0∗β̂ 1)̂ 

```{r confidence intervals }
dist_plot_1_df %>% 
  summarize(
    ci_lower_r_squared = quantile(r_squared, 0.025), 
    ci_upper_r_squared = quantile(r_squared, 0.975)) %>% 
  knitr::kable()

dist_plot_2_df %>% 
  summarize(
    ci_lower_log_alpha_beta = quantile(alpha_beta, 0.025), 
    ci_upper_log_alpha_beta = quantile(alpha_beta, 0.975)) %>% 
  knitr::kable()
```

### Problem 2

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r create dataset_1,  message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
    mutate(
        city_state = str_c(city, state, sep = "_"),
        victim_age = as.numeric(victim_age),
        resolution = case_when(
        disposition == "Closed without arrest" ~ 0,
        disposition == "Open/No arrest"        ~ 0,
        disposition == "Closed by arrest"      ~ 1,
      )
    ) %>% 
  filter(
    !city_state %in% c("Tulsa_AL", "Dallas_TX", "Phoenix_AZ", "Kansas City_MO"),
    victim_race %in% c("Black", "White")    
    ) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

Start with one city 

```{r regress_1}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore_MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

Do it for every city in the dataset.
First nest the dataset and then fit the dataset for each city.

```{r simulate_1}
models_results_df =
homicide_df %>%
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x,
                                family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

### Make a plot of the ORs

In each of these 50 cities are male homicide victims more or less likely to have homicide resolved by arrest compared to female victims.

```{r plot_1}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Problem 3

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r create dataset_2,  message = FALSE, warning = FALSE}
birthweight_df = 
  read_csv("data/birthweight.csv", na = c("", "NA", "Unknown")) %>% 
  janitor::clean_names() %>%
  mutate(
    sex = case_when(
        babysex == 1 ~ "female",
        babysex == 2 ~ "male"),
    father_race = case_when(
        frace == 1 ~ "White",
        frace == 2 ~ "Black",
        frace == 3 ~ "Asian",
        frace == 4 ~ "Puerto Rican",
        frace == 8 ~ "Other",
        frace == 9 ~ "Unknown"),
    malformations = case_when(
        malform == 0 ~ "absent",
        malform == 1 ~ "present"),
    mother_race = case_when(
        mrace == 1 ~ "White",
        mrace == 2 ~ "Black",
        mrace == 3 ~ "Asian",
        mrace == 4 ~ "Puerto Rican",
        mrace == 8 ~ "Other")
  ) %>% 
  mutate(
    sex = as.factor(sex),
    father_race = as.factor(father_race),
    malformations = as.factor(malformations),
    mother_race = as.factor(mother_race)
  ) %>% 
  select(-babysex, -frace, -malform, -mrace)
```












