---
title: "p8105_hw6_nt2607"
output: github_document
date: "2022-12-01"
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse)
library(p8105.datasets)
library(readr)
library(purrr)
library(modelr)
library(mgcv)
library(corrplot)
library(polycor)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)

```

### Problem 1

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.

```{r Loading the data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

Step 1. Fit the regression model 
Step 2. Check r-squared for the model
Step 3. Compute the log(β̂ 0∗β̂ 1)

```{r single}
#Fit regression
bootstrap_reg = lm(tmax ~ tmin, data = weather_df)
#Check r-squared for the model
bootstrap_reg %>% 
  broom::glance() %>% 
  select(r.squared) %>% 
  knitr::kable()

#Compute the log(β̂ 0∗β̂ 1̂) 
bootstrap_reg %>% 
  broom::tidy() %>% 
  select(term, estimate) %>%
  mutate(
    term = case_when(
      term == "(Intercept)" ~ "intercept",
      term == "tmin" ~ "tmin")) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
    ) %>% 
  mutate( alpha_beta = log(intercept*tmin))
```

Now build a bootstrap model for 5000 samples doing everything above.

```{r bootstrap}
bootstrap_weather_df =
weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
         square = map(models, broom::glance),
         results = map(models, broom::tidy)
         ) %>% 
  select(-strap, -models)
```

For each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

```{r plot and df 1}
dist_plot_1_df =
bootstrap_weather_df %>% 
  unnest(square) %>% 
  janitor::clean_names() %>% 
  select(r_squared)  # Step 5. produce estimates of these r-squared quantities.
  
dist_plot_1 =   
  dist_plot_1_df %>% 
  ggplot(aes(x = r_squared)) +
  geom_density()
dist_plot_1
```

Description - From the plot we can see that the r-squared values are almost normally distributed.




















