---
title: "p8105_hw6_nt2607"
output: github_document
date: "2022-12-01"
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse)
library(p8105.datasets)
library(readr)
library(purrr)
library(modelr)
library(mgcv)
library(corrplot)
library(polycor)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)

```

### Problem 1

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.

```{r Loading the data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

Step 1. Fit the regression model 
Step 2. Check r-squared for the model
Step 3. Compute the log(β̂ 0∗β̂ 1)

```{r single}
#Fit regression
bootstrap_reg = lm(tmax ~ tmin, data = weather_df)
#Check r-squared for the model
bootstrap_reg %>% 
  broom::glance() %>% 
  select(r.squared) %>% 
  knitr::kable()

#Compute the log(β̂ 0∗β̂ 1̂) 
bootstrap_reg %>% 
  broom::tidy() %>% 
  select(term, estimate) %>%
  mutate(
    term = case_when(
      term == "(Intercept)" ~ "intercept",
      term == "tmin" ~ "tmin")) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
    ) %>% 
  mutate( alpha_beta = log(intercept*tmin))
```

Now build a bootstrap model for 5000 samples doing everything above.

```{r bootstrap}
bootstrap_weather_df =
weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
         square = map(models, broom::glance),
         results = map(models, broom::tidy)
         ) %>% 
  select(-strap, -models)
```

For each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

For r-squared 
```{r plot and df 1}
dist_plot_1_df =
bootstrap_weather_df %>% 
  unnest(square) %>% 
  janitor::clean_names() %>% 
  select(r_squared)  # Step 5. produce estimates of these r-squared quantities.
  
dist_plot_1 =   
  dist_plot_1_df %>% 
  ggplot(aes(x = r_squared)) +
  geom_density()
dist_plot_1
```

Description - From the plot we can see that the r-squared values are almost normally distributed.

For  log(β̂ 0∗β̂ 1)
```{r df 2}
dist_plot_2_df =
bootstrap_weather_df %>% 
  unnest(results) %>% 
  janitor::clean_names() %>%
  select(id, term, estimate) %>% 
mutate(
    term = case_when(
      term == "(Intercept)" ~ "intercept",
      term == "tmin" ~ "tmin")) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate",
    id_cols = id
    ) %>% 
  mutate( alpha_beta = log(intercept*tmin)) %>% 
  select(alpha_beta) #produced estimates of log(β̂ 0∗β̂ 1)quantities
```

Plot the distribution of the log (β̂ 0∗β̂1) quantities

```{r plot 2}
dist_plot_2 = 
  dist_plot_2_df %>% 
  ggplot(aes(x = alpha_beta)) +
  geom_density() 
dist_plot_2
```

Description - From the plot we can see that the log of alpha*beta values are almost normally distributed. 

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2 and log(β̂ 0∗β̂ 1).

Confidence Intervals for r-squared value and  log(β̂ 0∗β̂ 1)̂ 

```{r confidence intervals }
dist_plot_1_df %>% 
  summarize(
    ci_lower_r_squared = quantile(r_squared, 0.025), 
    ci_upper_r_squared = quantile(r_squared, 0.975)) %>% 
  knitr::kable()

dist_plot_2_df %>% 
  summarize(
    ci_lower_log_alpha_beta = quantile(alpha_beta, 0.025), 
    ci_upper_log_alpha_beta = quantile(alpha_beta, 0.975)) %>% 
  knitr::kable()
```

### Problem 2

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r create dataset_1,  message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
    mutate(
        city_state = str_c(city, state, sep = "_"),
        victim_age = as.numeric(victim_age),
        resolution = case_when(
        disposition == "Closed without arrest" ~ 0,
        disposition == "Open/No arrest"        ~ 0,
        disposition == "Closed by arrest"      ~ 1,
      )
    ) %>% 
  filter(
    !city_state %in% c("Tulsa_AL", "Dallas_TX", "Phoenix_AZ", "Kansas City_MO"),
    victim_race %in% c("Black", "White")    
    ) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

Start with one city 

```{r regress_1}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore_MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Do it for every city in the dataset.
First nest the dataset and then fit the dataset for each city.

```{r simulate_1}
models_results_df =
homicide_df %>%
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x,
                                family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```












